\bf $\mathsf{TEDAT}$: Boosting Bandwidth-based Availability Over Inter-DC WAN

### 2021-01-18 paper.tex
introuction revision by Han

A \textit{one-size-fit-all} approach \cite{Teavar} ignoring these heterogeneities cannot support such SLAs well, and and may even hurt critical and uninterruptible applications when there are competitions on bandwidth. 

@@

Firstly, we advocate traffic engineering with \textit{bandwidth-based availability} (BA) provision: 
a BA demand $(d, \beta, \alpha, \gamma)$ means that it requests bandwidth $d$ for a life duration between $\alpha$ and $\gamma$, and should be ensured in at least a fraction $\beta$ of the duration, subjected to the network capacity and possible failures. Such a demand is typically represented by a Service Level Agreement (see Table \ref{target} for real world examples), and different users or applications may pose different demands. 
%a tenant's \textit{promised bandwidth of service $j$ should be available at least $\beta_j\%$ time}.  
%It tries to guarantee the bandwidth demands from tenants under network uncertainty.
We show that state-of-the-art traffic engineering schemes fail to the heterogeneous bandwidth-based availability demands in an economic manner, especially under diverse link failure probabilities that may vary by several orders of magnitude (see $\S$\ref{background}).
%meet services' bandwidth-based availability targets under arbitrarily link failures (see $\S$\ref{background}).
%This is due to the fact that these schemes either ignore the difference in link failure probabilities that can vary by several orders of magnitude in practice or fail to consider the diverse availability targets of services.
%The stronger availability can impel network to provide stable services.
%Compared with the connectivity-based availability, it makes a further step and tries to guarantee the minimal bandwidth demands under network uncertainty after the success of connections.
%
%Taking the diverse availability demands from different applications and the application importance into consideration,

@@

The admission control scheme 

@@

$\mathsf{TEDAT}$ strikes balance between efficiency and optimality, so that new demands can be admitted and guaranteed as much as possible with negligible delay.

@@

Then based on a linear programming model, our traffic scheduling algorithm sets up tunnels and allocates bandwidth for the admitted demand.

@@

At last, based on a mixed-integer linear programming model, the failure recovery procedure pre-computes backup bandwidth allocations and reroute traffic to minimize the revenue loss due to SLA violations, and is proved to be 2-optimal. 

>>>>

\textit{One-size-fit-all} approaches (e.g., TEAVAR \cite{Teavar})  ignoring these heterogeneities cannot support such SLAs well, and may even hurt critical and uninterruptible applications when there are competitions on bandwidth. 

@@

Firstly, we advocate traffic engineering with \textit{bandwidth-based availability} (BA) provision: 
a BA demand $(d, \beta, \alpha, \gamma)$ means that it requests bandwidth $d$ for a life duration between $\alpha$ and $\gamma$, and should be guaranteed at least $\beta\%$ of the duration, subjected to the network capacity and possible failures. Such a demand is typically represented by a Service Level Agreement (see Table \ref{target} for real world examples), and different users or applications may pose different demands. 
%a tenant's \textit{promised bandwidth of service $j$ should be available at least $\beta_j\%$ time}.  
%It tries to guarantee the bandwidth demands from tenants under network uncertainty.
We show that state-of-the-art traffic engineering schemes fail to meet the heterogeneous bandwidth-based availability demands, especially under diverse link failure probabilities that may vary by several orders of magnitude (see $\S$\ref{background}).
%meet services' bandwidth-based availability targets under arbitrarily link failures (see $\S$\ref{background}).
%This is due to the fact that these schemes either ignore the difference in link failure probabilities that can vary by several orders of magnitude in practice or fail to consider the diverse availability targets of services.
%The stronger availability can impel network to provide stable services.
%Compared with the connectivity-based availability, it makes a further step and tries to guarantee the minimal bandwidth demands under network uncertainty after the success of connections.
%
%Taking the diverse availability demands from different applications and the application importance into consideration,

@@

%The admission control scheme 

@@

The admission control strikes a good balance between efficiency and optimality, so that new demands can be admitted and guaranteed as much as possible with negligible delay.

@@

Then based on a Linear Programming (LP) model, our traffic scheduling algorithm allocates bandwidth for the admitted demands over tunnels.

@@

At last, based on a Mixed-Integer Linear Programming (MILP) model, the failure recovery procedure pre-computes backup bandwidth allocations and reroute traffic to minimize the revenue loss due to SLA violations.
We also propose a 2-approximation algorithm to solve it efficiently.
